---
title: "Biomass"
author: "Author Name? Anything of importance?"
date: "Last Update: `r format(Sys.time(), '%B %d, %Y')`"
output:
 html_document:
    toc: true
    toc_float:
      toc_collapsed: true
    toc_depth: 4
    number_sections: False
    theme: cosmo
    code_folding: 'hide'
    
---

# Examples of Structure

## Examples of Structure

### Examples of Structure

#### Examples of structure 

---

# Several Columns

<div class = "row">
  
<div class = "col-md-4">
<br><br>Since R Markdown use the [bootstrap framework](https://getbootstrap.com/docs/4.0/layout/grid/) under the hood. It is possible to benefit its powerful grid system. Basically, you can consider that your row is divided in 12 subunits of same width. You can then choose to use only a few of this subunits.
</div>
  
<div class = "col-md-4">
<br><br>Column number two can contain more text. Also, look at column number 3. We can embed images or code in some graphs.
</div>
  
<div class = "col-md-4">
```{r,  message=FALSE, echo=FALSE, warning=FALSE}
library(ggplot2)
ggplot( mtcars, aes(x=mpg)) + geom_histogram(fill="skyblue", alpha=0.5) + theme_minimal()
```
</div>
</div>



---

# Tabs

## Resolutions {.tabset}

Resolution can be defined in many different ways. Here, think of resolution as the degree of detail in a process or attribute. Remote sensing is centered around 4 distinct resolutions: Spatial, Spectral, Temporal, Radiometric.

### Spatial

Spatial Resolution refers to pixel size. The smaller the pixel size, the greater the definition of the image. For example, Landsat satellites capture data in 30m resolution. Each pixel is 90x90 feet in area. That's pretty big. My entire house and yard could fit in a single pixel. Looking at Landsat data, I could not be able to find my house. 

Some imagery has fine spatial resolution at 1m. I could easily pick out my home in a 1m pixel image. 

Spatial resolution is a primary driver in deciding what imagery to use for what analysis. A 30m spatial resolution image would be worthless if we are remotely sensing ant hills. A 1m spatial resolution would be terribly difficult to process if examining global processes. 

### Spectral

"Spectral resolution describes the ability of a sensor to define fine wavelength intervals. The finer the spectral resolution, the narrower the wavelength range for a particular channel or band". 

The higher the spectral resolution, the more analyses you can process.


### Temporal

Temporal resolution refers to the return-interval among satellites. Landsat satellites revolve the earth in 16 days. That means every 16 days the satellite passes over the same geographic location on Earth. 

Some imagery, like aerial imagery doesn't have a temporal resolution. It is simply collected when it is collected. 

Some satellites are fixed, meaning they are fixed over a specific location on Earth and rotate with the Earth, focusing on the same location constantly. These satellite have no temporal resolution.

### Radiometric

"The radiometric resolution of image data in remote sensing stands for the ability of the sensor to distinguish different grey-scale values. It is measured in bit. The more bit an image has, the more grey-scale values can be stored, and, thus, more differences in the reflection on the land surfaces can be spotted."

---

# Tables

```{r, warning=FALSE}
library(DT)
datatable(mtcars, rownames = FALSE, filter="top", options = list(pageLength = 5, scrollX=T) )
```

---

# Highlighting

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

- This is important
- So it is highlighted

</div>

---

# pdf

```{r}
xfun::embed_file("images/test.pdf")
```

